
\begin{abstract}
\underline{\textbf{Background:}} Software modernization is critical for organizations that need cost-effective solutions to deal with the rapid obsolescence of software and the increasing demand for new functionality.  In this context, the Object Management Group (OMG) promotes the Model Driven Development (MDD) concept and proposes the Architecture Driven Modernization (ADM) approach for model-based platform migration, which contains a set of standard representations of views on existing software systems. Several researchers have also been working on using ADM to modernize legacy systems. Thus, we argue that there is an essential need for evidence-based body of knowledge about different aspects of the adoption of ADM and its metamodels.
\underline{\textbf{Objectives:}} The main objective of this research is to conduct a systematic review study of the literature describing research into ADM. \underline{\textbf{Method:}} We undertook a systematic review study of the literature based upon searching of major electronic databases. \underline{\textbf{Results:}} We selected  30 primary studies and classified by their contribution, focus area and research type. Among these studies we found out a set of process and tool to aid the ADM. \underline{\textbf{Conclusion:}} ADM has become a popular approach for modernizing legacy systems by means of MDD. There is an overall positive perception about this approach. The findings provide interesting insights into different aspects of ADM. We expect that the findings can provide valuable information to readers on what can be expected from applying ADM and its metamodels to modernize a legacy systems. Furthermore, the results can provide insights for new research in the modernization area for investigating and defining new tools/process to assist the modernization of legacy system.
\end{abstract}
